### 2017-10-15 src/1_Introduction.tex
updating Financial info

The stochastic behaviour of financial time series, its incrementing
amount of data available and the need of performing accurate forecasting in
short periods of time has motivated researchers to create efficient and fast
algorithms. This study involves interdisciplinary knowledge such as: finance,
scientific computing, high performance computing, machine learning
among others.

@@

\textit{An online learning algorithms based on cointegration and high
performance computing will allow faster forecasting
algorithms for financial time series to be obtained while maintaining good accuracy levels.}

>>>>

The stochastic behaviour of financial time series, its incrementing
amount of data available and the need of performing accurate forecasting in
short periods of time has motivated researchers to create efficient and fast forecast
algorithms. This study involves interdisciplinary knowledge such as: finance,
scientific computing, high performance computing, machine learning
among others.

@@

\textit{An online learning algorithm based on cointegration and high
performance computing will allow faster forecasting
algorithms for financial time series to be obtained while maintaining good accuracy levels.}

### 2017-10-15 src/2_Finance.tex
updating Financial info

High frequency trading (HFT) strategies are based on buy and sell assets in
short periods of time gaining a small profit in every transaction despite the
transaction costs. The key is the amount of transactions that HFT algorithms are
capable to execute.  In 2012 more than 50\% of US market trades were HFT.  HFT
has motivated computer-driven strategies capable of processing large amount of
data in short periods of time.

@@

\begin{figure}[!h]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=\textwidth]{img/HFTtradestime}
  \caption[Holding time of an opened position of a high frequency trade]{Holding time of an opened position of a high frequency trade.Source
  \cite{aldridge2009}.}
  \label{fig:HFTtimes}
\end{figure}
In 2014 HFT represented nearly 50\% of equity trades in the US and more than
20\% in Europe showing a consistent fall since 2009 which was its best year. US
market revenues have fallen dramatically.  Figure~\ref{fig:HFTmarket} on the
left shows HFT trades percentage of US and Europe equity shares. The right
figure shows how revenues in US stocks have fallen the last years.

\begin{figure}[!h]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=\textwidth]{img/HFTmarket}
  \caption[HFT market share in the US and Europe]{Left figure shows HFT market share in the US and Europe. Right figure
  shows revenue in the US. Source: TABB Group.}
  \label{fig:HFTmarket}
\end{figure}
One of the reasons of this fall is that exchange markets have adapted, having
now faster, more transparent and efficient market structures than before.
This has been possible due to its investment in technology enhancing
reliability and stability of transactions. Even though this fall, HFT is still a major component of regulated markets and
will probably remain as a topic of interest for researchers in the near future.

>>>>

High frequency trading (HFT) strategies are based on buy and sell assets in
short periods of time gaining a small profit in every transaction despite the
transaction costs. The key is the amount of transactions that HFT algorithms are
capable to execute.  In 2016 nearly 50\% of US market trades were HFT.  HFT
has motivated computer-driven strategies capable of processing large amount of
data in short periods of time.

@@

\begin{figure}[!h]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=\textwidth]{img/HFTtradestime}
  \caption[Holding time of an opened position of a high frequency trade]{Holding time of an opened position of a high frequency trade. Source
  \cite{aldridge2009}.}
  \label{fig:HFTtimes}
\end{figure}
In 2016 HFT represented nearly 50\% of equity trades in the US showing a consistent fall since 2009, which was its best year, until 2013 where this rate remains the same until 2016.  Figure~\ref{fig:HFTmarket1} shows HFT trades percentage of US equity shares.

\begin{figure}[!h]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=\textwidth]{img/HFTmarket1.png}
  \caption[HFT market share in the US and Europe]{HFT market share in the US. Source: TABB Group.}
  \label{fig:HFTmarket1}
\end{figure}

\begin{figure}[!h]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=\textwidth]{img/HFTmarket2.png}
  \caption[Revenue in the US]{Revenue in the US. Source: TABB Group.}
  \label{fig:HFTmarket2}
\end{figure}
US market revenues have fallen dramatically. Figure~\ref{fig:HFTmarket2} shows how revenues in US stocks have fallen the last years. One of the reasons of this fall is that exchange markets have adapted, having
now faster, more transparent and efficient market structures than before.
This has been possible due to its investment in technology enhancing
reliability and stability of transactions. Even though this fall, HFT is still a major component of regulated markets and
will probably remain as a topic of interest for researchers in the near future.
